Where Do Events Come From?

### 2018-08-04 paper.tex
...

@@

We implemented an extensible runtime that exposes hooks for the interrupts and
power manager, which we validated in two microcontrollers: an
\emph{8-bit AVR/ATmega} and a \emph{32-bit ARM/Cortex-M0}.
%
We also implemented drivers for a variety of peripherals, such as GPIO, A/D
converter, USART, SPI, and nRF24L01 transceiver.
%
The applications built on top of these drivers show significant energy savings
due to automatic standby.

@@

Note that applications need not to be explicit about energy management to take
advantage of sleep modes.
All happens automatically because of the synchronous-reactive execution model
and energy-aware runtime of \CEU.

TODO: energy savings

@@

- CRP

@@

- electre

>>>>

%TODO: energy savings
%TODO: timers (mux, many impls, energy)

@@

We implemented an extensible runtime that exposes hooks for the interrupts and
power manager, which we validated in two microcontrollers: an
\emph{8-bit AVR/ATmega} and a \emph{32-bit ARM/Cortex-M0}.
%
We also implemented drivers for a variety of peripherals, such as GPIO, A/D
converter, USART, SPI, and nRF24L01 transceiver.
%
The applications built on top of these drivers show optimal energy savings due
to automatic standby.

@@

Note that applications need not to be explicit about energy management to take
advantage of sleep modes.
All happens automatically because of the synchronous-reactive execution model
and energy-aware runtime of \CEU.
Figure~\ref{fig.energy} shows our initial tests with five existing C/Arduino
applications rewritten in \CEU.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{energy}
\caption{ Energy consumption in \emph{mA} for five existing C/Arduino
          applications rewritten in \CEU.
\label{fig.energy}
}
\end{figure}

@@

\begin{comment}
- CRP

@@

- electre
\end{comment}
